\textbf{universal corpus}

### 2014-03-19 docs/computEL/liling.tex
added combined counts

\begin{table}
\centering
    \begin{tabular}{l|cc}
    ~         & \#Languages & \#Families \\ \hline
    ODIN      & 1218       & 101       \\
    Omniglot  & 134        & 21        \\
    UDHR      & 355        & 47        \\
    Wikipedia & 209        & 22       \\
    \end{tabular}
\caption{Corpus Coverage}
\end{table}

>>>>

\begin{table}
\centering
    \begin{tabular}{l|cc}
    ~         				& \#Languages & \#Families \\ \hline
    ODIN      				& 1218       & 101       \\
    Omniglot  				& 134        & 21        \\
    UDHR      				& 355        & 47        \\
    Wikipedia 				& 209        & 22       \\ \hline
    \textbf{Combined}	& 1347			 & 106 
    \end{tabular}
\caption{Corpus Coverage}
\end{table}
